Forcing for Isabelle

### 2018-12-29 LICS/isabelle.tex
comento este comentario

In this paper, locales have a further use. The \emph{Fundamental
  Theorems of Forcing} we use talk about a specific map $\forceisa$
from formulas to formulas. The definition of $\forceisa$ is involved
and we will not dwell on this now; but applications of those theorems
do not require to know how it is defined. Therefore, we black-box it
and pack everything in a locale that assumes that there is such a
map that satisfies the Fundamental Theorems.

\begin{description}
\item[\texttt{forcing\_notion}] preorden con top
\item[\texttt{countable\_generic}] lo anterior con una familia contable de densos.
\item[\texttt{M\_ZF}] axiomas.
\item[\texttt{forcing\_data}]: lo anterior contable transitivo y una notion.
\item[\texttt{forcing\_thms}]: eso.
\item[\texttt{G\_generic}]: lo anterior y G es genérico.
\item[\texttt{M\_extra\_assms}]: check in M e instancia de reemplazo para G.
\item[\texttt{G\_generic\_extra}]: los dos anteriores (no sé si sigue estando)
\end{description}

>>>>

In this paper, locales have a further use. The \emph{Fundamental
  Theorems of Forcing} we use talk about a specific map $\forceisa$
from formulas to formulas. The definition of $\forceisa$ is involved
and we will not dwell on this now; but applications of those theorems
do not require to know how it is defined. Therefore, we black-box it
and pack everything in a locale called \texttt{forcing\_thms} that
assumes that there is such a 
map that satisfies the Fundamental Theorems.

%% \begin{description}
%% \item[\texttt{forcing\_notion}] preorden con top
%% \item[\texttt{countable\_generic}] lo anterior con una familia contable de densos.
%% \item[\texttt{M\_ZF}] axiomas.
%% \item[\texttt{forcing\_data}]: lo anterior contable transitivo y una notion.
%% \item[\texttt{forcing\_thms}]: eso.
%% \item[\texttt{G\_generic}]: lo anterior y G es genérico.
%% \item[\texttt{M\_extra\_assms}]: check in M e instancia de reemplazo para G.
%% \item[\texttt{G\_generic\_extra}]: los dos anteriores (no sé si sigue estando)
%% \end{description}
